Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
conclusion
Changed median.

The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
time amounts to approximately $30$ minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. A link
to the full experimental environment, including scripts to reproduce the experiment, all
benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

The median runtime for our benchmark set is $197$\,s, implying that half of the controllers
can be synthesised in less than $5$ minutes using our present approach. Overall the average synthesis
time amounts to approximately $30$ minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. A link
to the full experimental environment, including scripts to reproduce the experiment, all
benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
